---
title: "01-review-wrangling"
output: html_document
---

```{r}
library(tidyverse)
library(writexl)
```

# Extracting reviews for analysis
## Our exclusion process
- we exclude tools that have fewer than 5 ratings (apple) or less than 100 installs / users (google play and chrome web)
- we exclude reviews with fewer than 10 words
- we want: broad distribution across functionality and stores
- we do, in order of the most popular: for a main functionality type, we slice off a tool from each store which has that type of functionality and sample up to 30 reviews from it; then we move on to the next functionality type; we repeat until we have about 1500 reviews

## Read in the review data
Get the reviews that have more than 10 words

```{r}
review_data <- read_csv(here::here("data", "processed", "distinct_reviews.csv")) %>% 
  mutate(review_word_count = stringi::stri_count_words(review_text)) %>% 
  filter(review_word_count >= 10) %>% 
  select(-review_word_count)
  
# get also the review counts
review_counts <- review_data %>% 
  group_by(tool_id) %>% 
  summarise(num_reviews = n())

```

## Get the tool info
We apply the exclusion criteria and order them by our ranking measure

```{r}
store_info <- read_csv(here::here("data", "processed", "meta_data_all_w_design_pattern_types.csv"))

# exclude if they have fewer than 5 ratings (apple) or less than 100 installs / users on the google play and chrome web stores
# arrange by numbers of users (num of ratings for the apple store)
tool_by_num_users <- store_info %>% 
  select(store, tool_id, title, average_rating, num_ratings, min_installs, num_users, categories_alphabetically) %>% 
  left_join(review_counts) %>% 
  filter(!is.na(num_reviews)) %>% 
  filter((store == "apple" & num_ratings >= 5) | min_installs >= 100 | num_users >= 100) %>% 
  mutate(ranking_measure = case_when(
    store == "play" ~ min_installs,
    store == "chrome" ~ num_users,
    store == "apple" ~ num_ratings
  )) %>% 
  arrange(store, desc(ranking_measure))
  
```

Ok, so let's write a nested for loop to grab the reviews.

```{r}
feature_categories <- c("Block/removal", "Goal-advancement", "Self-tracking", "Reward/punish")
stores <- c("apple", "chrome", "play")

# initialise empty results and apps sampled from
review_results <- tibble(
)
apps_sampled_from <- c()

while(nrow(review_results) < 1500){
  for (category in feature_categories){
    current_category_tools <- tool_by_num_users %>% 
      filter(!tool_id %in% apps_sampled_from) %>% 
      filter(str_detect(categories_alphabetically, category))
    
    for (cur_store in stores) {
      # print out how many we have and break the loop if we're about 1500
      print(str_c("num reviews sampled: ", nrow(review_results)))
      
      if(nrow(review_results) > 1500) {
        print("breaking loop")
        break
      }
      
      #print(cur_store)
      current_store_tools <- current_category_tools %>% 
        filter(store == cur_store)
      
      current_app <- current_store_tools %>% 
        slice(1) %>% 
        pull(tool_id)
      
      if (length(current_app) > 0){
        current_reviews <- review_data %>% 
          filter(tool_id == current_app) %>% 
          slice(1:30) %>% 
          slice_sample(n = 30, replace = FALSE)
        
        # update reviews and apps sampled from
        review_results <- bind_rows(review_results, current_reviews)
        apps_sampled_from <- c(apps_sampled_from, current_app) 
      }
    }
  }
}

```

We'll add a date to the reviews

```{r}
all_reviews_w_most_recent_date <- read_csv(here::here("data", "processed", "all_reviews.csv")) %>% 
  group_by(row_number()) %>% 
  top_n(1, date)

review_results %>% 
  mutate(review_id = str_c("R", row_number())) %>% 
  left_join(all_reviews_w_most_recent_date) %>% 
  left_join(store_info) %>% 
  select(review_id, store, title, tool_id, categories_alphabetically, user_name, date, rating, review_text) %>% 
  arrange(title, tool_id, date) %>% 
  write_xlsx(str_c(here::here("data", "processed/"), lubridate::today(), "-reviews_for_ta.xlsx"))

```

